Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-03 neurips-20/cvx-flats.tex
quick scan

We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
\raft{Added: $\Y$ is always finite for us.  Reminds me: we should state infinite $\Y$ as a major open problem}
The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
As we focus heavily on conditional distributions $D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with probability simplex $\simplex$, the set of all distributions over $\Y$.

@@

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex}
\raft{no other cites?  AA15 sort of counts I think} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
%\raft{Nice!  Love ``proxies'' here.}
In the case of a discrete target loss, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
%\raft{FYI Jessie: Two general points.  (1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.  Next time it would be more efficient if you made sure to balance local edits with global scans to catch these sorts of things, as well as making sure we aren't explaining things twice, etc.  (2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.  See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}\jessiet{Noted boss man}

@@

If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the regret with respect to $\ell$, the two definitions are equivalent. % for the appropriate choice of $\propdis$.
% when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
\begin{lemma}\label{lem:consistent-loss-implies-prop}
	Given a surrogate loss $L$, link $\psi$, and target loss $\ell$, set
	% Take $\propdis: \R \times \simplex \to \reals_+$ with 
  $\mu(r,p) := R_\ell(r,p)$.
  Then
	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}\btw{Don't \emph{need} $\prop{\ell}$ nonempty/nondegenerate here.}
\begin{proof}
	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
  Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
        \begin{align}
	  &\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
	  &\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
	  &\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
	\end{align}
        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
\end{proof}

@@

\begin{lemma}\label{lem:set-valued-prop-flats}
	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \simplex$\jessie{relint?} with reports $r,r' \in \R$ with $p \in \gamma_r \cap \gamma_{r'}$.
	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \implies F \subseteq \gamma_{r'}$.
\end{lemma}
\begin{proof}

@@

The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss with discrete predictions.
We now show that this bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
%\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now. \bo{Ideally we've explained the connection earlier and don't need to say it here.}}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
\citet{ramaswamy2016convex} construct what they call the subspace of feasible dimensions and give bounds in terms of its dimension.
\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ is the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
%  \raf{Let's simplify to $\epsilon \in (-\epsilon_0,\epsilon_0)$}
\end{definition}

%\bo{Jessie, if you have time, could you move everything but the corollary statement to the appendix, then (below the corollary statement) flesh out something like the following proof sketch? if you are pressed for time, let me know and I'll take a crack at it!
%\begin{itemize}
%  \item First consider $p \in \relint{\simplex}$.
%  \item If there is a codimension-$d$ flat in the level set containing $p$, then the feasible subspace definitely has dimension at least as large as the flat.
%  \item The completes the proof for $p \in \relint{\simplex}$ (explaining how Theorem 2 applies).
%  \item For other $p$, we show that the feasible subspace dimension is the same relative to the simplex on $\supp(p)$. Meanwhile any flat containing $p$ has only smaller codimension relative to $\supp{p}$. This extends the proof to this case.
%\end{itemize}
%} % END BO COMMENT
%\raf{Would also like to mention how our proof is shorter, even factoring in all the lemmas and theorem 2, since we don't have to deal with the infimum in calibration (the eplisons in their proof) and cut straight to the exact minimizers.}\jessie{took a crack at it and made a note}

\botodo{Felt like most of the proof details here would overlap unnecessarily with the proof sketch itself.}
%We regain the bounds provided by~\citet[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
%First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
%Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$.

It turns out that the subspace of feasible directions is, roughly, a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
\botodo{Avoided mentioning the lemma, since it's not in the main body.}
This allows us to prove the bound of \citet{ramaswamy2016convex}, Corollary~\ref{cor:fsd-bound}, in a shorter and (in our opinion) simpler way.
Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.

@@

In the proof of Theorem~\ref{thm:bayes-risk-lower-bound} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
\btw{Raf Note to self: need to sync the refs to the actual version on arxiv... or something...}
%\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
  Let $L$ elicit some $\Gamma:\simplex\to\reals^d$.
  Let $p\in\relint\simplex$ and let $\Gamma_r$ be some level set of $\Gamma$ such that
  (i) $p\in\Gamma_r$,
  (ii) $\codim(\affhull(\Gamma_r))=d$, and
  (iii) either $\Gamma_r$ is a singleton or $\lbar$ is nonconstant on $\Gamma_r$.
  Then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
\end{restatable}

@@

While this work tightens bounds on the dimension of consistent surrogate losses, it does not completely characterize the dimensionality of a convex surrogate for a given problem.
One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
\btw{Infinite $\Y$}

@@

\begin{proposition}
	When $\R$ is finite, a loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
\end{proposition}
\begin{proof}
	\jessiet{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
$\implies$
	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u L(u; p)$.
	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  
	Now we have $R_L(u_m; p \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
%	
% Commented out 05.19.2020 for easier proof if Lemma 5 is true.
%	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
%	
%	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
%	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
%	
%	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
%	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.

@@

Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below \jessiet{really just need lower semi-continuity and boundedness from below} of the surrogate loss, since we can take the constant sequence at the (attained) infimum.
%
%\jessie{$D \implies A$, but actually $\lnot B \wedge C \implies \lnot D$}
%Fix $p \in \simplex$.
%Suppose we have a sequence $\{\epsilon_m\}$ so that $\epsilon_m \to 0$, but $\zeta(\epsilon_m) \not \to 0$.
%If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
%We can now construct the sequence $\{\epsilon'_m\}$ with $\epsilon'_m = \lim_{j \to \infty} R_L(u^j_m, p)$.
%This sequence converges to $0$, but we have $\lim_{m \to \infty} \zeta(\epsilon'_m) = \lim_{m \to \infty} \lim_{j \to \infty} \zeta(R_L(u^j_m, p)) \not \to 0$. 
%As $R_\ell(\psi(u_m); p) \leq R_L(u_m; p)$ for all $m$, we then have this being true in the limit.
%For this sequence, this then gives a loose bound of $0 \leq \lim_{m\to\infty} R_\ell(\psi(u_m); p) \leq c$. 
%	
\end{proof}

\subsection{Relating calibration, consistency, and indirect elicitation.}
Even with the more general notion of calibration that extends beyond discrete predictions, we still have consistency implying calibration.
\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later; also, should this be a lemma instead of a proposition?}
	%  \raft{Do we define ``continuous loss''?  Maybe ``(not necessarily discrete)'' is clearer.}
\end{proposition}
\begin{proof}
	We show the contrapositive.
	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
	Suppose $D \sim \X \times\Y$ has only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D f(X,Y) = \E_p f(x, Y)$.
	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
	\raft{Type error with $D=D_x$; see AA15 for how they phrase \jessie{better?}}
	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
\end{proof}

Moreover, we have calibration implying indirect elicitation.
\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
	As $p \in \Gamma_u$, then $\zeta(\exploss{L}{u}{p} - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
\end{proof}

@@

\btw{Bo: I assume this will go to the appendix}
\begin{lemma}[\citep{frongillo2018elicitation}]
	\label{lem:elic-complex-bayes-concave}
	Suppose the loss $L$ elicits $\Gamma:\simplex\to\R$.
	Let $\lbar$ be the Bayes risk of $L$.
	Then for any $p,p'\in\simplex$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
\end{lemma}

>>>>

We consider supervised learning problems in the space $\X \times \Y$, for some \emph{feature space} $\X$ and a finite \emph{label space} $\Y$, with data drawn from a distribution $D$ over $\X \times \Y$.
The task is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} $\R$, which may be different from $\Y$.
For example, in ranking problems $\R$ may be all $n!$ permutations over the $n$ labels forming $\Y$.
As we focus heavily on conditional distributions $D_x = \Pr[Y|X=x]$ over $\Y$ given some $x \in X$, we often abstract away $x$, working directly with probability simplex $\simplex$, the set of all distributions over $\Y$.

@@

Various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration~\citep{agarwal2015consistent,ramaswamy2016convex} and property elicitation~\citep{frongillo2015vector-valued,fissler2016higher,frongillo2018elicitation}.
%\raft{Nice!  Love ``proxies'' here.}
In the case of a discrete target loss, \citet{ramaswamy2016convex} introduce \emph{convex calibration dimension}, the minimum prediction dimension yielding a convex calibrated surrogate.
Their results has led to the design of consistent convex surrogates for discrete prediction problems such as hierarchical classification~\citep{ramaswamy2015hierarchical} and classification with an abstain option~\citep{ramaswamy2018consistent}.
%\raft{FYI Jessie: Two general points.  (1) I spent the majority of my time in this section just on dependencies; e.g.\ you had ``similar to elicitation complexity mentioned above'' but elicitation complexity was not mentioned above.  Next time it would be more efficient if you made sure to balance local edits with global scans to catch these sorts of things, as well as making sure we aren't explaining things twice, etc.  (2) You tend to mix background with nods to our results, which is actually good to do, but it can be jarring if you go back and forth too much.  See for example how I changed the previous subsection, reserving the nod to our work to the end of the subsection.}\jessiet{Noted boss man}

@@

If $\gamma$ is a property elicited by a target loss $\ell$, then taking $\propdis$ to be the regret with respect to $\ell$, the two definitions are equivalent. % for the appropriate choice of $\propdis$.
% when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
\begin{lemma}\label{lem:consistent-loss-implies-prop}
	Given a surrogate loss $L$, link $\psi$, and target loss $\ell$, set
	% Take $\propdis: \R \times \simplex \to \reals_+$ with 
  $\mu(r,p) := R_\ell(r,p)$.
  Then
	$(L, \psi)$ is consistent with respect to $\ell$ if and only if $(L,\psi)$ is $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
  \btw{Note: don't actually $\gamma$ nonempty here.}
\end{lemma}
\begin{proof}
	First, observe that $\propdis(r,p) = 0 \iff \exploss{\ell}{r}{p} = \inf_{r' \in \R} \exploss{\ell}{r'}{p} \iff r \in \gamma(p)$.
	Now suppose $(L, \psi)$ are consistent with respect to $\ell$, and take any sequence $\{f_m\}$ of measurable hypotheses.
  Rewriting the right-hand side of Definition~\ref{def:consistent-ell},
        \begin{align}
	  &\; \E_D \ell(\psi \circ f_m(X), Y)\to \inf_f \E_D \ell(\psi \circ f(X), Y)   \label{eqn:cons-loss-cond} \\
	  &\iff \E_X R_\ell(\psi \circ f_m(X), D_X) \to 0                               \nonumber  \\
	  &\iff \E_X \propdis(\psi \circ f_m(X), D_X) \to 0~.~                          \label{eqn:cons-prop-cond}
	\end{align}
        Therefore, $\mathbb{E}_D L(f_m(X),Y) \to \inf_f \mathbb{E}_D L(f(X),Y)$ implies (\ref{eqn:cons-loss-cond}) if and only if it implies (\ref{eqn:cons-prop-cond}).
\end{proof}

@@

\begin{lemma}\label{lem:set-valued-prop-flats}
	Suppose we are given an elicitable property $\gamma : \simplex \toto \R$ and distribution $p \in \relint\simplex$ such that $p \in \gamma_r \cap \gamma_{r'}$ for $r,r' \in \R$.
	Then for any flat $F$ containing $p$, $F \subseteq \gamma_r \iff F \subseteq \gamma_{r'}$.
\end{lemma}
\begin{proof}

@@

The main known technique for lower bounds on surrogate dimensions is given by \citet{ramaswamy2016convex} for the quadrant of a target loss with discrete predictions.
We now show that this bound follows relatively directly from Theorem \ref{thm:cvx-flats}.
%\citet{ramaswamy2016convex} give lower bounds on the convex calibration dimension, or equivalently the dimension of a convex and consistent surrogate\jessiet{should probably cite the original calibration iff consistent in discrete setting result; have it earlier in the paper now. \bo{Ideally we've explained the connection earlier and don't need to say it here.}}, by constructing what they call the subspace of feasible dimensions and giving bounds in terms of its dimension.
\citet{ramaswamy2016convex} construct what they call the subspace of feasible dimensions and give bounds in terms of its dimension.
\begin{definition}[Subspace of feasible directions]\label{def:subspace-feas}
	The \emph{subspace of feasible directions} $\Sc_\C(p)$ of a convex set $\C \subseteq \reals^n$ at a point $p \in \C$ is the subspace $\Sc_\C(p) = \{ v \in \reals^n : \exists \epsilon_0 > 0 $ such that $p + \epsilon v \in \C \; \forall \epsilon \in (-\epsilon_0,\epsilon_0) \}$.
\end{definition}

It turns out that the subspace of feasible directions is, roughly, a special case of a flat described by Theorem~\ref{thm:cvx-flats}.
This allows us to prove the bound of \citet{ramaswamy2016convex}, Corollary~\ref{cor:fsd-bound}, in a shorter and (in our opinion) simpler way.
Due to the infimum in the definition of calibration, the original proof requires careful taking of sequences and the approximate subdifferentials, while indirect elicitation allows us to work with exact minimizers of the surrogate.
\raft{Revisit this sentence!}

@@

In the proof of Theorem~\ref{thm:bayes-risk-lower-bound} below, we modify the argument of~\citet[Corollary 7]{frongillo2018elicitation} to bound the convex elicitation complexity of the Bayes risk of the loss.
\raft{Note to self: need to sync the refs to the actual version on arxiv... or something...}
%\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
\begin{restatable}{theorem}{bayesrisklowerbound}\label{thm:bayes-risk-lower-bound}
  Let $L$ elicit some $\Gamma:\simplex\to\reals^d$.
  Let $p\in\relint\simplex$ and let $\Gamma_r$ be some level set of $\Gamma$ such that
  (i) $p\in\Gamma_r$,
  (ii) $\codim(\affhull(\Gamma_r))=d$, and
  (iii) either $\Gamma_r$ is a singleton or $\lbar$ is nonconstant on $\Gamma_r$.
  Then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
\end{restatable}

@@

While this work tightens bounds on the dimension of consistent surrogate losses, it does not completely characterize the dimensionality of a convex surrogate for a given problem.
One might be able to further tighten these bounds by property elicitation by studying monotonicity and adjacency of level sets.
In discrete predictions, these bounds might also be tightened if the equivalence of convex calibration dimension and embedding dimension of~\citet{finocchiaro2020embedding} is shown; the current embedding dimension bounds are not tight either, but additional structure is imposed by considering the embedding framework.
Lastly, the practical reason why consistency is desired is to ensure the guarantee of empirical risk minimization (ERM) rates; however, the relationship between ERM rates and property elicitation has not been studied.
\raft{Infinite $\Y$}

@@

\begin{proposition}
	When $\R$ is finite, a loss and link $(L, \psi)$ are calibrated with respect to a target loss $\ell$ via Definition~\ref{def:calibrated-general} if and only if calibration via Definition~\ref{def:calibrated-finite}.
\end{proposition}
\begin{proof}
	\btw{Old proof commented out; simplified using Lemma~\ref{lem:calib-converging-regrets}}
$\implies$
	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
	If $(L, \psi)$ are not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then there is a $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} \exploss{L}{u}{p} = \inf_u L(u; p)$.
	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  
	Now we have $R_L(u_m; p \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, so by Lemma~\ref{lem:calib-converging-regrets}, we contradict calibration by Definition~\ref{def:calibrated-general}.
%	
% Commented out 05.19.2020 for easier proof if Lemma 5 is true.
%	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.
%	
%	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
%	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.
%	
%	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
%	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.

@@

Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below of the surrogate loss,
\btw{really just need lower semi-continuity and boundedness from below}
since we can take the constant sequence at the (attained) infimum.
%
%\jessie{$D \implies A$, but actually $\lnot B \wedge C \implies \lnot D$}
%Fix $p \in \simplex$.
%Suppose we have a sequence $\{\epsilon_m\}$ so that $\epsilon_m \to 0$, but $\zeta(\epsilon_m) \not \to 0$.
%If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
%We can now construct the sequence $\{\epsilon'_m\}$ with $\epsilon'_m = \lim_{j \to \infty} R_L(u^j_m, p)$.
%This sequence converges to $0$, but we have $\lim_{m \to \infty} \zeta(\epsilon'_m) = \lim_{m \to \infty} \lim_{j \to \infty} \zeta(R_L(u^j_m, p)) \not \to 0$. 
%As $R_\ell(\psi(u_m); p) \leq R_L(u_m; p)$ for all $m$, we then have this being true in the limit.
%For this sequence, this then gives a loose bound of $0 \leq \lim_{m\to\infty} R_\ell(\psi(u_m); p) \leq c$. 
%	
\end{proof}

\subsection{Relating calibration, consistency, and indirect elicitation.}
Even with the more general notion of calibration that extends beyond discrete predictions, we still have consistency implying calibration.
\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
\end{proposition}
\begin{proof}
	We show the contrapositive.
	If $(L, \psi)$ are not calibrated with respect to $\ell$, then there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
	Suppose $D \sim \X \times\Y$ has only one $x \in \X$ with $Pr_D(X = x) > 0$ so that $p := D_x$ and $\E_D f(X,Y) = \E_p f(x, Y)$.
	Consider any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$.
	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi \circ f(X), Y) \not \to \inf_f \E_D \ell(\psi \circ f(X), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$.
\end{proof}

Moreover, we have calibration implying indirect elicitation.
\begin{lemma}\label{lem:calib-implies-indir}
	If a surrogate and link $(L, \psi)$ are calibrated with respect to a loss $\ell:\R \times\Y \to \reals$, then $L$ indirectly elicits the property $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	Let $\Gamma$ be the unique property directly elicited by $L$, and fix $p \in \simplex$ with $u$ such that $p \in \Gamma_u$.
  \raft{Use $\Gamma(p) \neq \emptyset$ here!}
	As $p \in \Gamma_u$, then $\zeta(\exploss{L}{u}{p} - \risk{L}(p)) = \zeta(0) = 0$, we observe the bound $\ell(\psi(u); p) \leq \risk{\ell}(p)$.
	We also have $\ell(\psi(u); p) \geq \risk{\ell}(p)$ by definition of $\risk{\ell}$, so we must have $\ell(\psi(u);p) = \risk{\ell}(p) = \ell(\gamma(p); p)$, and therefore, $p \in \gamma_{\psi(u)}$.
	Thus, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$, so $L$ indirectly elicits $\gamma$.
\end{proof}

@@

\begin{lemma}[\citep{frongillo2018elicitation}]
	\label{lem:elic-complex-bayes-concave}
	Suppose the loss $L$ elicits $\Gamma:\simplex\to\R$.
	Let $\lbar$ be the Bayes risk of $L$.
	Then for any $p,p'\in\simplex$ with $\Gamma(p)\neq\Gamma(p')$, we have $\lbar(\lambda p + (1-\lambda) p') > \lambda \lbar(p) + (1-\lambda) \lbar(p')$ for all $\lambda\in(0,1)$.
\end{lemma}
